New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-08 Manuscript/Manuscript.Rmd
IS results

Introduction text goes here. You can change the name of the section if
necessary using `\introduction[modified heading]`.

The following settings can or must be configured in the header of this
file and are bespoke for Copernicus manuscripts:

-   The `journal` you are submitting to using the official abbreviation.
    You can use the function
    `rticles::copernicus_journal_abbreviations(name = '...')` to search
    the existing journals.

-   Specific sections of the manuscript:

    -   `running` with `title` and `author`

    -   `competinginterests`

    -   `copyrightstatement` (optional)

    -   `availability` (strongly recommended if any used), one of
        `code`, `data`, or `codedata`

    -   `authorcontribution`

    -   `disclaimer`

    -   `acknowledgements`

**Please note:** Per [their
guidelines](https://publications.copernicus.org/for_authors/manuscript_preparation.html),
Copernicus does not support additional \LaTeX{} packages or new \LaTeX{}
commands than those defined in their `.cls` file. This means that you
cannot add any extra dependencies and a warning will be thrown if so.\
This extends to syntax highlighting of source code. Therefore this
template sets the parameter `highlight` in the YAML header to `NULL` to
deactivate Pandoc syntax highlighter. This prevent addition of external
packages for highlighting inserted by Pandoc. However, it might be
desirable to have syntax highlight available in preprints or for others
reasons. Please see `?rmarkdown::pdf_document` for available options to
activate highlighting.

@@

### Interaction strength estimation

@@

The main equation we used for estimating the interaction strength IS is:

```{=tex}
\begin{equation}
IS = \alpha x_R \frac{m_R}{m_C}
\end{equation}
```

@@

@@

In order to individually characterize the species of the food web, we considered weighted and unweighted properties (Figure 2). The former is based on the estimation of the interaction strength described in the previous section. The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014]. As weighted property we took into account the mean interaction strength, meaning the average strength of all interactions. As unweighted properties we used: a) degree or the total number of trophic interactions, taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.

@@

All analyses were performed in R software, using packages igraph [@Csardi2005], cheddar [@Hudson2013], and multiweb [@Saravia2019]. The source code and data are available at https://github.com/EcoComplex/WeddellSea.

@@

The Weddell Sea food web comprises 490 species and 16041 predator-prey interactions (Figure 3).

@@

Figure of distribution IS
Model fit

@@

>>>>

Introduction text goes here.

@@

### Interaction strength estimation and distribution

@@

The main equation we used for estimating the interaction strength IS is:
```{=tex}
\begin{equation}
IS = \alpha x_R \frac{m_R}{m_C}
\end{equation}
```

@@

Finally, we fit the distribution of the interaction strengths of the food web considering six candidate models (Uniform, Normal, Exponential, Power-law, log-Normal and Gamma) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion [@Burnham2002].

@@

In order to individually characterize the species of the food web, we considered weighted and unweighted properties (Figure 2). The former is based on the estimation of the interaction strength described in the previous section. The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].

As weighted property we took into account the mean interaction strength, meaning the average strength of all interactions. After exploring the distribution of the interaction strength among the species of the food web, we decided to apply the k-means clustering method, which aims to partition the species into k groups such that the sum of squares from points to the assigned cluster centres is minimized [@Hartigan1979].

As unweighted properties we used: a) degree or the total number of trophic interactions, taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.

@@

All analyses were performed in R software, mainly using packages igraph [@Csardi2005], cheddar [@Hudson2013], and multiweb [@Saravia2019]. The source code and data are available at https://github.com/EcoComplex/WeddellSea.

@@

In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions (Figure 3).

@@

The distribution of the interaction strength best fit to a log-Normal model, which indicates that there is a prevalent skew towards weaker interactions (Figure 4, Table 1). Regarding the distribution of the mean interaction strength among the species of the food web, the clustering method shows that species can be classified in two groups: 'High' and 'Low' interaction strength.

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490)."}
knitr::include_graphics("IS_dist.jpg")
```

```{=tex}
\begin{table}[t]
\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web. According to AIC, log-Normal is the best model.}
\begin{tabular}{l c c c}
\tophline

Model & df & AIC & deltaAIC \\
\middlehline
log-Normal & 2 & -356579 & 0 \\
\middlehline
Gamma & 2 & -352575 & 4004 \\
\middlehline
Power-law & 2 & -347646 & 8933 \\
\middlehline
Exponential & 1 & -262852 & 93726 \\
\middlehline
Normal & 2 & -222785 & 133793 \\
\middlehline
Uniform & 2 & -178001 & 178578 \\

\bottomhline
\end{tabular}
\end{table}
```

@@

"Low functional redundancy at key trophic levels makes these ecosystems (polar pelagic) particularly sensitive to change". [@Murphy2016]

### 2022-08-08 Manuscript/Manuscript.tex
IS results

Introduction text goes here. You can change the name of the section if
necessary using
\texttt{\textbackslash{}introduction{[}modified\ heading{]}}.

The following settings can or must be configured in the header of this
file and are bespoke for Copernicus manuscripts:

\begin{itemize}
\item
  The \texttt{journal} you are submitting to using the official
  abbreviation. You can use the function
  \texttt{rticles::copernicus\_journal\_abbreviations(name\ =\ \textquotesingle{}...\textquotesingle{})}
  to search the existing journals.
\item
  Specific sections of the manuscript:

  \begin{itemize}
  \item
    \texttt{running} with \texttt{title} and \texttt{author}
  \item
    \texttt{competinginterests}
  \item
    \texttt{copyrightstatement} (optional)
  \item
    \texttt{availability} (strongly recommended if any used), one of
    \texttt{code}, \texttt{data}, or \texttt{codedata}
  \item
    \texttt{authorcontribution}
  \item
    \texttt{disclaimer}
  \item
    \texttt{acknowledgements}
  \end{itemize}
\end{itemize}

\textbf{Please note:} Per
\href{https://publications.copernicus.org/for_authors/manuscript_preparation.html}{their
guidelines}, Copernicus does not support additional \LaTeX{} packages or
new \LaTeX{} commands than those defined in their \texttt{.cls} file.
This means that you cannot add any extra dependencies and a warning will
be thrown if so.\\
This extends to syntax highlighting of source code. Therefore this
template sets the parameter \texttt{highlight} in the YAML header to
\texttt{NULL} to deactivate Pandoc syntax highlighter. This prevent
addition of external packages for highlighting inserted by Pandoc.
However, it might be desirable to have syntax highlight available in
preprints or for others reasons. Please see
\texttt{?rmarkdown::pdf\_document} for available options to activate
highlighting.

@@

\subsubsection{Interaction strength estimation}

@@

@@

In order to individually characterize the species of the food web, we
considered weighted and unweighted properties (Figure 2). The former is
based on the estimation of the interaction strength described in the
previous section. The latter is related to properties commonly used in
qualitative (presence/absence of interaction) food web studies
\citep{Martinez1991, Dunne2002, Borrelli2014}. As weighted property we
took into account the mean interaction strength, meaning the average
strength of all interactions. As unweighted properties we used: a)
degree or the total number of trophic interactions, taking into account
in- and out-interactions (role as predator and prey, respectively); b)
trophic level or the position in the food web relative to primary
producers/detritus; and c) trophic similarity or the trophic overlap
between species based on shared and unique resources and consumers.

@@

All analyses were performed in R software, using packages igraph
\citep{Csardi2005}, cheddar \citep{Hudson2013}, and multiweb
\citep{Saravia2019}. The source code and data are available at
https://github.com/EcoComplex/WeddellSea.

@@

Figure of distribution IS Model fit

@@

@@

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-5}
\end{figure}

>>>>

Introduction text goes here.

@@

\subsubsection{Interaction strength estimation and distribution}

@@

Finally, we fit the distribution of the interaction strengths of the
food web considering six candidate models (Uniform, Normal, Exponential,
Power-law, log-Normal and Gamma) using maximum likelihood
\citep{McCallum2008}, and selected the model performance by computing
the Akaike Information Criterion \citep{Burnham2002}.

@@

In order to individually characterize the species of the food web, we
considered weighted and unweighted properties (Figure 2). The former is
based on the estimation of the interaction strength described in the
previous section. The latter is related to properties commonly used in
qualitative (presence/absence of interaction) food web studies
\citep{Martinez1991, Dunne2002, Borrelli2014}.

As weighted property we took into account the mean interaction strength,
meaning the average strength of all interactions. After exploring the
distribution of the interaction strength among the species of the food
web, we decided to apply the k-means clustering method, which aims to
partition the species into k groups such that the sum of squares from
points to the assigned cluster centres is minimized
\citep{Hartigan1979}.

As unweighted properties we used: a) degree or the total number of
trophic interactions, taking into account in- and out-interactions (role
as predator and prey, respectively); b) trophic level or the position in
the food web relative to primary producers/detritus; and c) trophic
similarity or the trophic overlap between species based on shared and
unique resources and consumers.

@@

All analyses were performed in R software, mainly using packages igraph
\citep{Csardi2005}, cheddar \citep{Hudson2013}, and multiweb
\citep{Saravia2019}. The source code and data are available at
https://github.com/EcoComplex/WeddellSea.

@@

The distribution of the interaction strength best fit to a log-Normal
model, which indicates that there is a prevalent skew towards weaker
interactions (Figure 4, Table 1). Regarding the distribution of the mean
interaction strength among the species of the food web, the clustering
method shows that species can be classified in two groups: `High' and
`Low' interaction strength.

\begin{figure}
\includegraphics[width=12cm]{IS_dist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490).}\label{fig:unnamed-chunk-4}
\end{figure}

\begin{table}[t]
\caption{Model comparison (AIC) for the distribution of interaction strengths of the Weddell Sea food web.}
\begin{tabular}{l c c c}
\tophline

Model & df & AIC & deltaAIC \\
\middlehline
log-Normal & 2 & -356579 & 0 \\
\middlehline
Gamma & 2 & -352575 & 4004 \\
\middlehline
Power-law & 2 & -347646 & 8933 \\
\middlehline
Exponential & 1 & -262852 & 93726 \\
\middlehline
Normal & 2 & -222785 & 133793 \\
\middlehline
Uniform & 2 & -178001 & 178578 \\

\bottomhline
\end{tabular}
\end{table}

@@

``Low functional redundancy at key trophic levels makes these ecosystems
(polar pelagic) particularly sensitive to change''. \citep{Murphy2016}

@@

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-6}
\end{figure}
